---
title: "Crop data"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Packages

```{r packages}
require(data.table)
require(sf)
require(mapview)
require(stringr)
require(dplyr)
require(data.table)
require(ggplot2)
require(leaflet)
```

## Harvest data
(1) A list named fl_vec of every name of the datatables in the data/nrw directory was created 
(2) A new list named l was created
(3-5) Every table from the data named as the strings in the list fl_vec was implemented in a dataframe named dat
(6) The first row  was dropped, but why?
(7) The names for the first two columns representing the district number and the district name were set to 'rs' and 'gen'
(8) The list l was filled with the rows, each containing a dataframe from dat for every year
(9) the names of the rows in l are reduced from the data name to only the yearnumber
(10) rbindlist stacked all the data.frames of the list l to a single data.frame and labeled the id column to year

```{r data-harvest}
# read list of files
fl_vec = list.files('data/nrw', pattern = 'csv', full.names = TRUE)
l = list()
for (i in seq_along(fl_vec)) {
  fl = fl_vec[i]
  dat = fread(fl, skip = 7, header = TRUE, encoding = 'Latin-1', stringsAsFactors = FALSE)
  dat = dat[-1, ]
  setnames(dat, 1:2, c('rs', 'gen'))
  
  l[[i]] = dat
  names(l)[i] = gsub('ernte|.csv', '', basename(fl))
}
# bind list of data.table to one data.table
dt = rbindlist(l, fill = TRUE, idcol = 'year')

# TODO remove special symbols and convert column types to numeric
dtc = data.frame(dt)
for(i in 4:41){
  dtc[,i] =  gsub('[-.x]','0',dtc[,i])
  dtc[,i] = gsub('[,]','.',dtc[,i])
}
for(i in 4:41){
  dtc[,i] = as.numeric(dtc[,i])
}
# TODO bring data into long format (year, rs, gen as identifier variables)
crop_names = colnames(dtc[,4:41])
setDT(dtc)
str(dtc)
dtc_long = melt(dtc, id.vars = c("year","rs","gen"), measure.vars = crop_names, variable.name = 'crop', value.name = 'dt.ha' )
```

(1) Shapefiles der Kreise Deutschlands werden eingelesen.
(2) Namen der Spalten werden alle nun klein geschrieben
(3) rs der Kreise soll als numeric typisiert sein --> merge mit rs aus dtc
(4) kreis2 ist Tabelle aus Kopie der Spalten rs, rs_alt, ... von kreis
(5) zeigt die Karte an

```{r data-spatial-regions}
kreis = st_read(file.path('data', 'germany_kreis.shp'), stringsAsFactors = FALSE)
setnames(kreis, tolower(names(kreis)))
kreis$rs = as.numeric(kreis$rs)
kreis2 = kreis[ , names(kreis) %in% c('rs', 'rs_alt', 'geom', 'shape_leng', 'shape_area') ]
mapview(kreis2) # to have an interactive look at the geo data
# TODO refine to NRW only
kreis3 = kreis2[0,]
# kreis3 = as.data.frame[0,]
for (i in 1:402){
  if (kreis2$rs[i]>5000 & kreis2$rs[i]<6000){
  # add_row(kreis3)
    rbind(kreis3)
  kreis3[nrow(kreis3)+1,] = kreis2[i,]
  }
}
mapview(kreis3) # test in mapview
```

```{r merge}
# TODO merge geo and crop data
fin = merge(kreis3, dtc_long)
str(fin) #test structure

# https://r-spatial.github.io/sf/reference/tidyverse.html
#Syntax Beispiel 
# Ersten zwei Zeichen von RS sind das Bundesland
#   kreis = kreis %>% 
#     mutate(rs2 = substr(RS,1,2)) # adds new variable and preserves existing ones
#   # Fläche pro Bundesland
#   kreis %>% 
#     group_by(rs2) %>% 
#     mutate(mn = mean(SHAPE_AREA)) # adds new variable and preserves existing ones
#   kreis %>% 
#     group_by(rs2) %>% 
#     summarise(mn = mean(SHAPE_AREA)) # summarises variables

# Durchschnittsertrag je Feldfrucht in ganz NRW
mn_crop = fin %>% 
  group_by(crop) %>%
  summarise(mn_dt=mean(dt.ha))

ggplot(mn_crop, aes(crop,mn_dt)) + 
  geom_bar() 
  


# Durchschnittsertrag je Kreis
mn_kreis = fin %>%
  group_by(rs) %>%
  summarise(mn_dt = mean(dt.ha), do_union = TRUE)

plot(mn_kreis["mn_dt"])

# TODO Durchschnittsertrag je Kreis pro Fläche
mn_kreispa = fin %>%
  group_by(rs) %>%
  summarise(mn_dt.ha.a = mean(dt.ha)^2/mean(shape_area), do_union = TRUE)

plot(mn_kreispa["mn_dt.ha.a"])

# TODO Durchschnittsertrag je Feldfrucht je Kreis 
mn_cropkreis = fin %>%
  group_by(rs) %>%
  
# TODO Durchschnittsertrag je wichtige Feldfrucht pro Fläche
```

```{r data-spatial-pesticides}
nrw2 = readRDS(file.path('data/nrw', 'nrw_sites.rds')) # spatial sites data
nrw_sam = readRDS(file.path('data/nrw', 'nrw_samples.rds')) # pesticide samples
```

## Tasks

- Part1:
  - Clean crop data
  - Merge with spatial data
  - Aggregate crop data
  - Select 5-10 regions (i.e. Kreis) with the most agriculture
  - Visualize regions with intensive agriculture

- Part2:
  - Intersect with pesticide sampling sites
  - Look if sites with high concentrations intersect well with regions (i.e. Kreis) with high agriculture
  - Visualise this

- Document this in R-Markdown
- Presentation?





