---
title: "Crop data"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Packages

```{r packages}
require(data.table)
require(sf)
require(mapview)
```

## Harvest data
(28) A list named fl_vec of every name of the datatables in the data/nrw directory was created 
(29) A new list named l was created
(30-32) Every table from the data named as the strings in the list fl_vec was implemented in a dataframe named dat
(33) The first row  was dropped, but why?
(34) The names for the first two columns representing the district number and the district name were set to 'rs' and 'gen'
(36) The list l was filled with the rows, each containing a dataframe from dat for every year
(37) the names of the rows in l are reduced from the data name to only the yearnumber and are reffered to as year
(40) rbindlist stacked all the data.frames of the list l to a single data.frame 

```{r data-harvest}
# read list of files
fl_vec = list.files('data/nrw', pattern = 'csv', full.names = TRUE)
l = list()
for (i in seq_along(fl_vec)) {
  fl = fl_vec[i]
  dat = fread(fl, skip = 7, header = TRUE, encoding = 'Latin-1', stringsAsFactors = FALSE)
  dat = dat[-1, ]
  setnames(dat, 1:2, c('rs', 'gen'))
  
  l[[i]] = dat
  names(l)[i] = gsub('ernte|.csv', '', basename(fl))
}
# bind list of data.table to one data.table
dt = rbindlist(l, fill = TRUE, idcol = 'year')

# TODO remove special symbols and convert column types to numeric

# 1. Try
dtc=data.frame(dt[,-1:-3]) #dropped first 3 columns to create new dataframe called dtc
for (i in seq_along(dtc)){
for (j in 1:671){
  dtc$i[j] <- sapply(dt$i[j], function(x) as.numeric(gsub("[.-x]", "", x)) ) 
  }
} #returns no changes in class and content
#if it works, then merge dtc with the first 3 rows of dt again

#2. Try
dtc2 = as.data.frame(lapply(dt[,4:41], function(x) as.numeric(gsub("[.-x]","",x))))
#returns only NA, even in columns 1 to 4

#3. Try


# TODO bring data into long format (year, rs, gen as identifier variables)
```

```{r data-spatial-regions}
kreis = st_read(file.path('data', 'germany_kreis.shp'), stringsAsFactors = FALSE)
setnames(kreis, tolower(names(kreis)))
kreis$rs = as.numeric(kreis$rs)
kreis2 = kreis[ , names(kreis) %in% c('rs', 'rs_alt', 'geom', 'shape_leng', 'shape_area') ]
mapview(kreis2) # to have an interactive look at the geo data
# TODO refine to NRW only
```

```{r merge}
# TODO merge geo and cropt data
```

```{r data-spatial-pesticides}
nrw2 = readRDS(file.path('data/nrw', 'nrw_sites.rds')) # spatial sites data
nrw_sam = readRDS(file.path('data/nrw', 'nrw_samples.rds')) # pesticide samples
```

## Tasks

- Part1:
  - Clean crop data
  - Merge with spatial data
  - Aggregate crop data
  - Select 5-10 regions (i.e. Kreis) with the most agriculture
  - Visualize regions with intensive agriculture

- Part2:
  - Intersect with pesticide sampling sites
  - Look if sites with high concentrations intersect well with regions (i.e. Kreis) with high agriculture
  - Visualise this

- Document this in R-Markdown
- Presentation?





