---
title: "Crop data"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Packages

```{r packages}
require(data.table)
require(sf)
require(mapview)
```

## Harvest data

```{r data-harvest}
# read list of files
fl_vec = list.files('data/nrw', pattern = 'csv', full.names = TRUE)
l = list()
for (i in seq_along(fl_vec)) {
  fl = fl_vec[i]
  dat = fread(fl, skip = 7, header = TRUE, encoding = 'Latin-1', stringsAsFactors = FALSE)
  dat = dat[-1, ]
  setnames(dat, 1:2, c('rs', 'gen'))
  
  l[[i]] = dat
  names(l)[i] = gsub('ernte|.csv', '', basename(fl))
}
# bind list of data.table to one data.table
dt = rbindlist(l, fill = TRUE, idcol = 'year')
# TODO remove special symbols and convert column types to numeric
# TODO bring data into long format (year, rs, gen as identifier variables)
```

```{r data-spatial-regions}
kreis = st_read(file.path('data', 'germany_kreis.shp'), stringsAsFactors = FALSE)
setnames(kreis, tolower(names(kreis)))
kreis$rs = as.numeric(kreis$rs)
kreis2 = kreis[ , names(kreis) %in% c('rs', 'rs_alt', 'geom', 'shape_leng', 'shape_area') ]
mapview(kreis2) # to have an interactive look at the geo data
# TODO refine to NRW only
```

```{r merge}
# TODO merge geo and cropt data
```

```{r data-spatial-pesticides}
nrw2 = readRDS(file.path('data/nrw', 'nrw_sites.rds')) # spatial sites data
nrw_sam = readRDS(file.path('data/nrw', 'nrw_samples.rds')) # pesticide samples
```

## Tasks

- Part1:
  - Clean crop data
  - Merge with spatial data
  - Aggregate crop data
  - Select 5-10 regions (i.e. Kreis) with the most agriculture
  - Visualize regions with intensive agriculture

- Part2:
  - Intersect with pesticide sampling sites
  
- Part3: Research question:
  - Do sites with high pesticide concentrations intersect well with regions (i.e. Kreis) with high agricultural intensity?
    - Visualization
  - Does agriculture intensity explain pesticide occurrence?
    - Regression models

- Document this in R-Markdown

- Presentation?

```{r}
kreis2 = st_transform(kreis, st_crs(nrw2))
st_crs(kreis2)
ggplot() +
  geom_sf(data = kreis2) +
  geom_sf(data = nrw2)
st_crs(nrw2)
mapview(list(kreis2, nrw2))





```



